Utilizing Google's Mobility Report to understand Infectious Disease Dynamics

### 2025-04-04 products/manuscript/Manuscript.qmd
Fixes

>>>>

On March 2nd, 2020, Governor Brian Kemp announces the first two confirmed COVID-19 cases in the state, a Father and Son returning from Italy. At the same time as the rest of the nation, March 11th, Governor Kemp announced a state of emergency and closed all public schools on March 16th indefinitely. In the span of the next two weeks, Georgia saw its first and hundredth death to the virus. Weeks later, on April 2nd, Governor Kemp announced a shelter in place order for all Georgia residents. After only a month, on April 30th, the shelter-in-place order expired allowing Georgians to go to gyms, salons, barberships, and shortly after, restaurants.
